Comparing Cross Validation Methods for Penalized Cox Regression

### 2017-09-18 cross-validation.tex
Comments on estimating baseline hazard for deviance resiudals

>>>>

When invented, both Martingale residuals and Deviance residuals were calculated only for observations that construct the baseline hazard, not for out-of-sample predictions. However, in the cross-validation context, residuals are calculated for observations that are not used to construct the baseline hazard. It is common to run into situations where some events in the test set occurred after the last event occured in the baseline, where the survival function dropped to 0. For those events, they would be treated as censored.
